\documentclass[a4paper,10pt]{article}

\usepackage[english]{babel}
\usepackage{framed}
\usepackage{pslatex}
\usepackage{url}


\newcommand\InstructionsPage[2]{%
  \newpage
  \thispagestyle{empty}

  \section*{How to connect to the Jupyter/IPython server}

  \begin{framed}
    \begin{center}
      \itshape Please keep this sheet until the end of tomorrow's training, \\
      as it contains credentials to connect to the server!
    \end{center}
  \end{framed}

  A Jupyter/IPython server will be used for some hands-on sessions. \\
  Here are instructions to connect.

  \begin{enumerate}
  \item Ensure your computer has internet access.
  \item Open a browser on the URL:
    \begin{quote}
      \url{https://AA.BB.CC.DD}
    \end{quote}
    {\small\textbf{Note:} Since this is a temporary installation, the server's
      HTTPS certificate has been self-signed. Browsers will flag this as a
      security risk and you will need to manually accept the certificate as
      ``trusted''. The procedure to do so varies from web browser to web
      browser; if in doubt, ask the instructors.}
    % {\small\textbf{Note:} the server's HTTPS certificate has been provided by the
    %   \emph{Let's encrypt} service, which is accepted by all major browsers since
    %   October 2015.  If your browser has not been updated since 2015, you will need
    %   to manually accept the certificate as ``trusted''.}
  \item Fill in the sign-in form with the following data:
    \begin{center}
      \begin{minipage}{0.75\linewidth}
        \setlength{\fboxsep}{0.5ex}
        \raggedright
        \textbf{Username:}
        \\
        \framebox[22em]{\raggedright #1}
        \\[1ex]
        \textbf{Password:}
        \\
        \framebox[22em]{\raggedright #2}
      \end{minipage}
    \end{center}
    \small
    \textbf{Note:}
    \begin{itemize}
    \item Passwords are case sensitive! Enter capital/small letters exactly as
      written.
    \item There are no spaces in passwords. Words are separated by a ``minus
      sign'' character.
    \item the Jupyter/IPython notebook is known \emph{not} to work with some
      versions of the Safari web browser (Apple's Mac OS X). Both Mozilla
      Firefox and Google Chrome are known to work well instead.
    \end{itemize}
  \end{enumerate}
}%

\begin{document}
\InstructionsPage{muster}{a-B-c-D}
%
\InstructionsPage{py01}{hided-xenophobic-Pyrenees-pagination}
\InstructionsPage{py02}{relating-thermoplastic-bays-applicants}
\InstructionsPage{py03}{officer-Donizetti-Wozzeck-causeless}
\InstructionsPage{py04}{gallstones-Dominic-mortician-mother}
\InstructionsPage{py05}{suffocated-Madison-acquiring-befouling}
\InstructionsPage{py06}{unsubscribing-mashed-ostriches-Wyo}
\InstructionsPage{py07}{committal-southbound-goal-bearers}
\InstructionsPage{py08}{regionally-swipe-disputation-sweet}
\InstructionsPage{py09}{superpower-crag-strikeouts-umbilicuses}
\InstructionsPage{py10}{obviously-Heep-suitable-misquoted}
\InstructionsPage{py11}{visualizing-pummel-exaggerate-mailings}
\InstructionsPage{py12}{Marvell-chemists-intellectuals-treadling}
\InstructionsPage{py13}{clandestine-cytoplasm-was-custards}
\InstructionsPage{py14}{smuggle-flora-hobbyhorses-endearingly}
\InstructionsPage{py15}{expects-Afrikaans-make-coincidentally}
\InstructionsPage{py16}{anaemic-fulfil-sodomites-pawned}
\InstructionsPage{py17}{steely-unceasingly-pretentiousness-darts}
\InstructionsPage{py18}{affix-supping-lammed-retiree}
\InstructionsPage{py19}{moonlighting-dishonesty-selfless-chanciest}
\InstructionsPage{py20}{shakers-rotational-commemorative-stewarding}
\InstructionsPage{py21}{harping-cleared-flagging-reedier}
\InstructionsPage{py22}{circus-coiled-lasagnas-motorcades}
\InstructionsPage{py23}{seepage-Frankie-squeaks-unrewarding}
\InstructionsPage{py24}{fashioning-cookie-origination-financially}
\InstructionsPage{py25}{soloist-kneaded-throng-inhalation}
\InstructionsPage{py26}{motivation-mace-stuccos-useless}
\InstructionsPage{py27}{specifics-mushiest-demises-painters}
\InstructionsPage{py28}{flapping-caudal-Connors-tailwind}
\InstructionsPage{py29}{eyeteeth-avenge-plagiarizes-caroling}
\InstructionsPage{py30}{rejoices-dodging-rewrites-chiropodist}
\InstructionsPage{py31}{uncountable-visioned-Blackfoot-synthetically}
\InstructionsPage{py32}{newels-wooden-Yaobang-tourmaline}
\InstructionsPage{py33}{astir-Crux-palpably-armorers}
\InstructionsPage{py34}{compactly-serpent-horsemen-depressing}
\InstructionsPage{py35}{ultraviolet-splatted-unorthodox-outlined}
\InstructionsPage{py36}{decreased-lamppost-graduation-Huxley}
\InstructionsPage{py37}{Geminis-dicta-prism-delicatessen}
\InstructionsPage{py38}{represent-enjoyment-Costello-Kurtis}
\InstructionsPage{py39}{furies-orthographic-architectures-Riefenstahl}
\InstructionsPage{py40}{reformulated-snippier-ruddier-strangest}
% \InstructionsPage{py41}{deodorized-albinos-miniatures-gimlet}
% \InstructionsPage{py42}{refreshment-Pygmalion-sympathetically-slaughter}
% \InstructionsPage{py43}{fireball-luridly-anatomists-intervenes}
% \InstructionsPage{py44}{southerly-heinously-honeycombing-ramify}
% \InstructionsPage{py45}{unbridled-glimpse-McVeigh-Uriah}
% \InstructionsPage{py46}{parading-Bollywood-desiring-educators}
% \InstructionsPage{py47}{shadowy-hangdog-brunet-cauterized}
% \InstructionsPage{py48}{Dutchman-involuntarily-documentation-immigrates}
% \InstructionsPage{py49}{isometric-terrorized-batches-bespoken}
% \InstructionsPage{py50}{splices-whats-wayfarers-Maiman}
% \InstructionsPage{py51}{teals-temptingly-ants-envoys}
% \InstructionsPage{py52}{abstaining-halitosis-derangement-perplexing}
% \InstructionsPage{py53}{fats-libation-languishes-medalists}
% \InstructionsPage{py54}{milieux-intellectualism-condensations-immortalizing}
% \InstructionsPage{py55}{Sirius-puncture-dislocate-hostelries}
% \InstructionsPage{py56}{preterites-freeloaded-kickback-lief}
% \InstructionsPage{py57}{nickel-resided-skirmishes-denigrate}
% \InstructionsPage{py58}{literals-noblewomen-bounding-priestly}
% \InstructionsPage{py59}{pause-Polaroid-characterizes-ulcers}
% \InstructionsPage{py60}{commissions-Mimosa-proportionals-conjoint}
% \InstructionsPage{py61}{legrooms-joyrides-brokerages-esoteric}
% \InstructionsPage{py62}{busily-scintillas-daddy-qualify}
% \InstructionsPage{py63}{Stein-noises-befog-scruff}
% \InstructionsPage{py64}{finisher-laxatives-paraphrases-disproved}
% \InstructionsPage{py65}{hay-magic-hindquarters-reimbursement}
% \InstructionsPage{py66}{penetrated-bakeries-proselytize-spools}
% \InstructionsPage{py67}{congruities-Rojas-bucks-externals}
% \InstructionsPage{py68}{penknives-frustrating-woolgathering-mergansers}
% \InstructionsPage{py69}{selectman-gripped-blonds-stairwell}
% \InstructionsPage{py70}{persuades-firehouse-Rte-installations}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
